### 2021-11-30 newvariant.tex
done?

There is currently a (minor) discrepancy in the estimates of relative strength of new variants, particularly for the Alpha variant.
Mathematical analyses have typically reported greater than a 1.4 fold increase in reproduction number for the Alpha variant ($\rho > 1.4$) whereas an independent analysis of secondary attack rates from contact tracing data suggests a 1.25--1.4 fold increase \citep{ukinvest}.
As shown in \cite{davies2021estimated} and \cite{volz2021transmission}, propagating uncertainty in generation interval estimates (and, in particular, assuming shorter generation intervals) can partially explain these differences:
For example, if we consider short and wide generation interval estimates from Tianjin, China ($\Gw=\Gv=2.57\days$ and $\kappa=1$; \cite{ganyani2020estimating}), we obtain $\rho=1.26$ (from $\delta=0.1\pday$ and $\rw = 0\pday$).
Although these estimates are more consistent with the attack rate analysis \citep{ukinvest},
we do not claim that they are necessarily more accurate.
While individual-level data from contact tracing can provide a more reliable source of information about the transmissibility and time scale of transmission in some cases, they can also be biased towards particular types of contacts---for example, household contacts are probably more likely to be identified---which could also affect the estimate of $\rho$.
Instead, this calculation simply highlights the importance of carefully considering generation-interval distributions in assessing the relative strength and speed of SARS-CoV-2 variants.
While we relied on parameter estimates for the Alpha variant throughout our analysis, our qualitative conclusions can be applied to studying other SARS-CoV-2 variants, including the Delta variant.

@@

We mostly considered idealized interventions of constant strength  or constant speed. Real interventions are likely more complex.
Interventions that reduce contact rates, such as social distancing measures and vaccination, are generally strength-like, but they can also elicit awareness-based behavioral responses that are speed-like---for example, infected individuals may self-isolate faster after symptom onset.
On the other hand, the hazard of isolation-based interventions (and thus, speed-like), such as contact tracing, can vary over the course of infection depending on delays in tracing infected individuals \citep{fraser2004factors,ferretti2020quantifying,scarabel2021renewal}.
Their effectiveness can further depend on the ``coverage'' of isolation, which is strength-like---for example, there may be a group of individuals that cannot be isolated by certain interventions due to asymptomaticity or the lack of participation in the contact tracing program.
Analyses of SARS-CoV-2 dynamics have primarily relied on the constant-strength framework \citep{gostic2020practical,unwin2020state,brauner2021inferring}, even when modeling speed-like interventions such as self-isolation \citep{flaxman2020Rt,brett2020transmission}.
While the constant-strength framework provides a convenient tool for modeling and understanding epidemic dynamics, we encourage researchers to consider both strength- and speed-based perspectives, as they can lead to different conclusions.

>>>>

There is currently a (minor) discrepancy in the estimates of relative strength of new variants, particularly for the Alpha variant.
Mathematical analyses have typically reported greater than a 1.4 fold increase in reproduction number for the Alpha variant ($\rho > 1.4$) whereas an independent analysis of secondary attack rates from contact tracing data suggests a 1.25--1.4 fold increase \citep{ukinvest}.
As shown in \cite{davies2021estimated} and \cite{volz2021transmission}, propagating uncertainty in generation interval estimates (and, in particular, assuming shorter generation intervals) can partially explain these differences:
For example, if we consider short and wide generation interval estimates from Tianjin, China ($\Gw=\Gv=2.57\days$ and $\kappa=1$; \cite{ganyani2020estimating}), we obtain $\rho=1.26$ (from $\delta=0.1\pday$ and $\rw = 0\pday$).
Although these estimates are more consistent with the attack rate analysis \citep{ukinvest},
we do not claim that they are necessarily more accurate.
While individual-level data from contact tracing can provide a more reliable source of information about the transmissibility and time scale of transmission in some cases, they can also be biased towards particular types of contacts---for example, household contacts are probably more likely to be identified---which could also affect the estimate of $\rho$.
Instead, this calculation simply highlights the importance of carefully considering generation-interval distributions in assessing the relative strength and speed of SARS-CoV-2 variants.
We relied on parameter estimates for the Alpha variant throughout our analysis, but our qualitative conclusions can be applied to studying other SARS-CoV-2 variants, including the Delta variant.

@@

Other studies have also tried to explain apparent changes in their estimates of relative strength using generation-interval-based arguemtns but sometimes gave inaccurate explanations. 
For example, Volz \textit{et al.} estimated that the relative strength of the Alpha variant declined in England between December 2020 and January 2021 \cite{volz2021transmission};
they hypothesized that a shorter generation interval of the Alpha variant could explain this phenomenon by reducing the relative speed (and therefore, the relative strength) under intervention measures.
However, our analysis suggests that a shorter generation interval of a new variant cannot explain the decline in relative strength.
Under a constant-strength intervention, the relative speed decreases (as predicted by  \cite{volz2021transmission}) but the relative strength remains constant (\fref{control_sim}B). 
Under a constant-speed intervention, the relative speed remains constant (\fref{control_sim}F), but the relative strength increases because the intervention will have a smaller effect on the variant with a shorter generation interval (\fref{control_sim}E).

We mostly considered idealized interventions of constant strength or constant speed.
Real interventions are likely more complex.
Interventions that reduce contact rates, such as social distancing measures, are generally strength-like, but they can also elicit awareness-based behavioral responses that are speed-like---for example, infected individuals may self-isolate faster after symptom onset.
Other strength-like interventions, such as vaccination, can also have disproportionately smaller effects on new variants depending on their antigenic variability.
On the other hand, the hazard of isolation-based interventions (and thus, speed-like), such as contact tracing, can vary over the course of infection depending on delays in tracing infected individuals \citep{fraser2004factors,ferretti2020quantifying,scarabel2021renewal}.
Their effectiveness can further depend on the ``coverage'' of isolation, which is strength-like---for example, there may be a group of individuals that cannot be isolated by certain interventions due to asymptomaticity or the lack of participation in the contact tracing program.
Analyses of SARS-CoV-2 dynamics have primarily relied on the constant-strength framework \citep{gostic2020practical,unwin2020state,brauner2021inferring}, even when modeling speed-like interventions such as self-isolation \citep{flaxman2020Rt,brett2020transmission}.
While the constant-strength framework provides a convenient tool for modeling and understanding epidemic dynamics, we encourage researchers to consider both strength- and speed-based perspectives, as they can lead to different conclusions.
